Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2020-01-24 IJCAR2020/absoluteness.tex
Arreglos muy pavos. Comentario sobre definiciones sintetizadas.

Once this class versions of the axioms are set up, it is not hard to
apply our synthesis method to obtain their internal, first-order
counterparts.
\begin{framed}
  Some code for axiom synthesis.
\end{framed}

>>>>

Once this class versions of the axioms are set up, it is not hard to
apply our synthesis method to obtain their internal, first-order
counterparts.\footnote{It should be noted that our method for
  synthetic definition requires that the schematic goal had a
  particular format where the only unbound schematic variable occurs
  as an (open) formula whose satisfaction is equivalent to some
  relativized predicate.}
\begin{framed}
  Some code for axiom synthesis.
\end{framed}

### 2020-01-24 IJCAR2020/conclusion.tex
Arreglos muy pavos. Comentario sobre definiciones sintetizadas.

We consider that the formalization of the definition of $\forceisa$
and its recursive characterization of forcing for atomic formulas is
turning point
in our project; the reason for this is that all further
developments will not involve such a daunting metamathematical
component. Even the proofs of the Fundamental Theorems of Forcing
turned out to follow rather smoothly after this initial setup was
ready, the only complicated affair being to show that various dense sets belong
to $M$. 
\begin{framed}
  Actually, this is a point to taken care of: the machinery of
  absoluteness and relativization must be developed for every new
  concept that is introduced.
\end{framed}

>>>>

We consider that the formalization of the definition of $\forceisa$
and its recursive characterization of forcing for atomic formulas is
a turning point
in our project; the reason for this is that all further
developments will not involve such a daunting metamathematical
component. Even the proofs of the Fundamental Theorems of Forcing
turned out to follow rather smoothly after this initial setup was
ready, the only complicated affair being to show that various dense sets belong
to $M$. 
\begin{framed}
  Actually, this is a point to taken care of: the machinery of
  absoluteness and relativization must be developed for every new
  concept that is introduced.
\end{framed}
